О множествах точек на плоскости с целочисленными расстояниями

### 2019-06-27 pps-linear-bound/pps-linear-lower-bound.tex
Proofreading by Usachev - p. 14

\begin{problem}
	\label{prb:minimal_shape}
	What is the minimal shape $\mathcal{S}$ such that any $M\in\mathfrak{M}(2,\mathbb{N})$ with $\operatorname{diam} M = d$
	is situated in  $\mathcal{S}$?
\end{problem}
This problem is another generalization of Lemma~\ref{lem:square_container}.
We know that $\mathcal{S}$ is not a circle of diameter $d$
(the counterexample is an equilateral triangle of side length $d$)
and we conjecture that $\mathcal{S}$ is not a Reuleaux triangle of width $d$
(the probable counterexample belongs to a circle of diameter $d$, see Theorem~\ref{thm:rational_set_on_circle}).

The solution of Problem~\ref{prb:minimal_shape} (if ever found) will lead to a sophisticated packing problem,
something like ``How to put $n$ points in a convex hull of concentric circle and Reuleaux triangle?''
Obviously, Problem~\ref{prb:minimal_shape} can be generalized to higher dimensions.

For $n=3,4,5$, there are optimal sets in $\mathfrak{M}(2,n)$ that contain distance 1
(see Remarks~\ref{rem:planar_set_with_minimeter_1_of_3_points} and~\ref{rem:planar_set_with_minimeter_1_of_4_and_5_points}).
However, we can put forward the following conjecture.
\begin{conjecture}
	\label{con:no_optimal_with_edge_1}
	Every set $M\in\mathfrak{M}(2,n)$, $n\geq 6$, such that for some $M_1,M_2$ equality $|M_1 M_2|=1$ holds,
	is not optimal.
\end{conjecture}

The motivation of Conjecture~\ref{con:no_optimal_with_edge_1} is based on the results of~\cite[Section 5]{kurz2008minimum},
especially the following theorem.

@@

For planar integral point sets containing distance 1, we can put forward the following problem.
\begin{problem}
	For given $n\geq 3$ and squarefree number $q \neq 1$,
	is there $M\in\mathfrak{M}(2,n)$, such that characteristic of $M$ is $q$
	and distance 1 occurs in $M$?
\end{problem}

When we talk about integral point sets containing distance 1 in higher dimensions, another problem arises.

>>>>

\begin{problem}
	\label{prb:minimal_shape}
	What is the minimal shape $\mathcal{S}$ such that any $M\in\mathfrak{M}(2,\mathbb{N})$ with $\operatorname{diam} M = d$
	is situated in  $\mathcal{S}$?
\end{problem}
This problem is another generalization of Lemma~\ref{lem:square_container}.
We know that $\mathcal{S}$ is not a circle of diameter $d$
(the counterexample is an equilateral triangle of side length $d$)
and we conjecture that $\mathcal{S}$ is not a Reuleaux triangle of width $d$
(the possible counterexample belongs to a circle of diameter $d$, see Theorem~\ref{thm:rational_set_on_circle}).

The solution to Problem~\ref{prb:minimal_shape} (if ever found) will lead to a sophisticated packing problem,
something like ``How to put $n$ points in a convex hull of concentric circle and Reuleaux triangle?''
Obviously, Problem~\ref{prb:minimal_shape} can be generalized to higher dimensions.

For $n=3,4,5$, there are optimal sets in $\mathfrak{M}(2,n)$ that contain distance 1
(see Remarks~\ref{rem:planar_set_with_minimeter_1_of_3_points} and~\ref{rem:planar_set_with_minimeter_1_of_4_and_5_points}).
However, we can suggest the following conjecture.
\begin{conjecture}
	\label{con:no_optimal_with_edge_1}
	Every set $M\in\mathfrak{M}(2,n)$, $n\geq 6$, such that for some $M_1,M_2$ equality $|M_1 M_2|=1$ holds,
	is not optimal.
\end{conjecture}

The motivation for Conjecture~\ref{con:no_optimal_with_edge_1} is based on the results of~\cite[Section 5]{kurz2008minimum},
especially the following theorem.

@@

For planar integral point sets containing distance 1, we can emphasise on the following problem.
\begin{problem}
	For given $n\geq 3$ and squarefree number $q \neq 1$,
	is there $M\in\mathfrak{M}(2,n)$, such that characteristic of $M$ is $q$
	and distance 1 occurs in $M$?
\end{problem}

The consideration of integral point sets containing distance 1 in higher dimensions gives a rise to another problem.
